An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-02-27 journal/poly-embed.tex
Clarified a point of confusion
Fixed proof of Prop 3 to be loss-based

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}~,
  \end{equation*}
  for all $p\in\simplex$.
  Combining with the above, we now have $\risk{L} = \risk{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

@@

	1 $\Rightarrow$ 2:
        \jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:elicitable-level-sets}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}

        Let $L$ elicit $\Gamma$.  
        If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  
		Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

        We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:elicitable-level-sets} and a corollary of the embedding definition).
        Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  
        Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

%	2 $\Rightarrow$ 1:
%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
%	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
%	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

%	1 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional by Lemma~\ref{lem:embedded-level-sets-trim} and equality of the set of embedded level sets of $\Gamma$ and set of level sets of $\gamma$.  Take $\Theta = \trim(\Gamma)$.}
%	Assume $\Gamma$ embeds a finite property $\gamma$.
%	Then for each $r \in \R$, we have $\Gamma_{\varphi(r)} = \gamma_r$, and therefore $\{\Gamma_{\varphi(r)} : r \in \R\} = \{\gamma_r : r \in \R\}$.
%	Chaining this with Lemma~\ref{lem:embedded-level-sets-trim}, we have $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
%	
%	\jessie{This is really the beginning of 2 $\Rightarrow 3$}
%	If there is a level set $\Gamma_{\varphi(\hat r)} \in \trim(\Gamma)$ that is not full-dimensional, then we can define an injection $\varphi'$ so that $\varphi' :\R \setminus \{\hat r\} \to \reals^d$ maps $r \mapsto \varphi(r)$.
%	(Iterate if there are multiple level sets that are not full-dimensional.)
%	Now take $\Theta = \{\Gamma_{\varphi'(r)} : r \in \R\}$.
%	We know each level set in $\Theta$ is full-dimensional by construction, and just need to show $\cup \Theta = \simplex$.
%	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}
	2 $\Rightarrow$ 3:
	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }

	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.

	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma = \Gamma|_{\varphi(\R)}$.}
    Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.

@@

\proposedadd{ADDITIONS HERE:}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	\begin{itemize}
		\item [$\subseteq$] As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional. For all $r \in \R$, we know $\gamma_r = \gamma_{\varphi(r)}$ by the definition of embedding, so $\Gamma_{\varphi(r)} \in \trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}.
		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
		Thus, we cannot observe this case.
	\end{itemize}
\end{proof}

\begin{lemma}\label{lem:fdls-in-trim}
	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	Let $u$ be the report such that $\theta = \Gamma_u$.
	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
\end{proof}

\begin{lemma}\label{lem:elicitable-level-sets}
	Let $\Gamma$ be an elicitable property.
	For all $p \in \simplex$, we have $|\Gamma(p)| > 1 \iff \exists r \in \Gamma(p)$ such that $\Gamma_{r'} \subseteq \Gamma_r$ for all $r' \in \Gamma(p)$.
\end{lemma}
\begin{proof}
	\jessie{TODO: argument on subgradients of the concave score over the loss.}
\end{proof}

@@

>>>>

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
	\jessie{Intuition: $\implies$: Take the injection given, and show there is a property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$. Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that there a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.  Losses match by considering $\risk{\ell}(\delta_y) = \risk{L}(\delta_y) = \ell(\gamma(\delta_y))_y = L(\varphi(\gamma(\delta_y)))_y$ for all $y \in \Y$. }
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Combining with the above, we now have $\risk{L} = \risk{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
	\jessie{Intuition: $\impliedby$: There are a finite set of full-dimensional level sets, which we enumerate, define a finite property, and take the discrete loss values equal to original loss values at the enumerated points.}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

@@

	1 $\Rightarrow$ 2:
        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}

        Let $L$ elicit $\Gamma$.  
        If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ eliciting $\gamma$ by Lemma~\ref{lem:embed-defs-equiv}. 		
        We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:embedded-level-sets-trim} and a corollary of the embedding definition).
        Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  
        Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

	2 $\Rightarrow$ 1:
	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

%	1 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional by Lemma~\ref{lem:embedded-level-sets-trim} and equality of the set of embedded level sets of $\Gamma$ and set of level sets of $\gamma$.  Take $\Theta = \trim(\Gamma)$.}
%	Assume $\Gamma$ embeds a finite property $\gamma$.
%	Then for each $r \in \R$, we have $\Gamma_{\varphi(r)} = \gamma_r$, and therefore $\{\Gamma_{\varphi(r)} : r \in \R\} = \{\gamma_r : r \in \R\}$.
%	Chaining this with Lemma~\ref{lem:embedded-level-sets-trim}, we have $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
%	
%	\jessie{This is really the beginning of 2 $\Rightarrow 3$}
%	If there is a level set $\Gamma_{\varphi(\hat r)} \in \trim(\Gamma)$ that is not full-dimensional, then we can define an injection $\varphi'$ so that $\varphi' :\R \setminus \{\hat r\} \to \reals^d$ maps $r \mapsto \varphi(r)$.
%	(Iterate if there are multiple level sets that are not full-dimensional.)
%	Now take $\Theta = \{\Gamma_{\varphi'(r)} : r \in \R\}$.
%	We know each level set in $\Theta$ is full-dimensional by construction, and just need to show $\cup \Theta = \simplex$.
%	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}

	1 $\Rightarrow$ 3: Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
	As the risks are equal, this is also true for $\Gamma$.
	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

%	2 $\Rightarrow$ 3:
%	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }
%		
%	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
%	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
%	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
%	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
%	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
%	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.

	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
    Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.

@@

\proposedadd{ADDITIONS HERE:}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.

	As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional. For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

	Second, $\Gamma_u = \Gamma_{\varphi(r)}$ for some $r \in \R$, then the level set is in both $\{\Gamma_{\varphi(r)} : r \in \R\}$ and $\trim(\Gamma)$.
%		
%		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
%		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
%		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
%		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
%		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
%		Thus, we cannot observe this case.
%	\end{itemize}
\end{proof}

\begin{lemma}\label{lem:embed-defs-equiv}
	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
\end{proof}

%\begin{lemma}\label{lem:fdls-in-trim}
%	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
%\end{lemma}
%\begin{proof}
%	Let $u$ be the report such that $\theta = \Gamma_u$.
%	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
%	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
%	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
%	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
%	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
%\end{proof}

@@

	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}
